Pteropod physiological analysis

### 2018-03-23 figures.Rmd
stressor mods created in dat_proc
all effects plots done

data(envdat)
data(ptedat)

@@

biomod <- rda(ptephy, envphy)

@@

phymod <- rda(ptephy, envphy)

@@

RDA plots:
```{r rda_plt, fig.height = 4.5, fig.width = 9}
# globals
coord_fix <- F
repel <- F
addsize <- 3
alpha <- 0.8
arrow <- 0.3
cols <- 'lightblue'

p1a <- ggord(biomod, ptslab = T, parse = T, repel = repel, coord_fix = coord_fix, addsize = addsize, size = dat_bio$Lat, sizelab = 'Latitude', alpha = alpha, arrow = arrow, ellipse = F) + 
  ggtitle('(a) Cellular stressors')
p2a <- ggord(phymod, ptslab = T, parse = T, repel = repel, coord_fix = coord_fix, addsize = addsize, size = dat_phy$Lat, sizelab = 'Latitude', alpha = alpha, arrow = arrow, ellipse = F) + 
  ggtitle('(b) Physiological stressors')

@@

# Code to override clipping
gt <- ggplot_gtable(ggplot_build(p))
gt$layout$clip[gt$layout$name == "panel"] <- "off"
grid.draw(gt)
```

>>>>

data(envdat)
data(ptedat)
data(phymod)
data(biomod)

@@

biorda<- rda(ptephy, envphy)

@@

phyrda <- rda(ptephy, envphy)

@@

```{r rdaplo, fig.height = 4.5, fig.width = 9}
# globals
coord_fix <- F
repel <- F
addsize <- 3
alpha <- 0.8
arrow <- 0.3
cols <- 'lightblue'

p1a <- ggord(biorda, ptslab = T, parse = T, repel = repel, coord_fix = coord_fix, addsize = addsize, size = dat_bio$Lat, sizelab = 'Latitude', alpha = alpha, arrow = arrow, ellipse = F) + 
  ggtitle('(a) Cellular endpoints')
p2a <- ggord(phyrda, ptslab = T, parse = T, repel = repel, coord_fix = coord_fix, addsize = addsize, size = dat_phy$Lat, sizelab = 'Latitude', alpha = alpha, arrow = arrow, ellipse = F) + 
  ggtitle('(b) Physiological endpoints')

@@

# Code to override clipping
gt <- ggplot_gtable(ggplot_build(p))
gt$layout$clip[gt$layout$name == "panel"] <- "off"
grid.draw(gt)
```
Fig. 2 Correlation matrix of environmental variables, cellular response endpoints, and population (abundance) and physiological response endpoints for pteropods.  Darker red values are strong positive correlations and darker purple values are strong negative correlations.  Significance values at alpha = 0.05 are shown by stars (p < 0.05 \*, p < 0.005 \*).

```{r effbio, fig.height = 8, fig.width = 9}
# cellular 92 (lpx, ara, ph - syn), 101 (lpx, ara, t - neg add), 164 (sod, ara, t, neg but no thrsh) 
biosel <- biomod %>% 
  filter(Model %in% paste0('mod', c(92, 101, 164))) %>% 
  dplyr::select(-data)

cols <- RColorBrewer::brewer.pal(9, 'RdBu')

##
# plots

# mod 92 cell (lpx, ara, ph - syn)
pl1 <- filter(biosel, grepl('92$', Model)) %>% 
  .$Modobj %>% 
  .[[1]] %>% 
  get_pldat(., 'pH')

p1 <- ggplot() +
  geom_line(data = pl1[[1]], aes(x = Ara, y = LPX, group = pH, colour = pH), size = 1) + 
  geom_text(data = pl1[[2]], aes(x= x, y = y, label = lab), hjust = 0) +
  theme_bw() +
  scale_x_continuous(expression(Omega[Ar])) +
  scale_colour_gradientn(colours = cols) + 
  scale_y_continuous('LPX') +
  ggtitle("(a) Synergistic effect of pH on aragonite\nsaturation")

# mod 101 cell (lpx, ara, t - neg add), 164 (sod, ara, t, neg but no thrsh) 
pl2 <- filter(biosel, grepl('101$', Model)) %>% 
  .$Modobj %>% 
  .[[1]] %>% 
  get_pldat(., 'Temp')

p2 <- ggplot() +
  geom_line(data = pl2[[1]], aes(x = Ara, y = LPX, group = Temp, colour = Temp), size = 1) + 
  geom_text(data = pl2[[2]], aes(x= x, y = y, label = lab), hjust = 0) +
  theme_bw() +
  scale_x_continuous(expression(Omega[Ar])) +
  scale_colour_gradientn(colours = cols) + 
  scale_y_continuous('LPX') +
  ggtitle("(b) Negative additive effect below threshold of\n temperature on aragonite saturation")

# mod 164 cell (sod, ara, t, neg but no thrsh) 
pl3 <- filter(biosel, grepl('164$', Model)) %>% 
  .$Modobj %>% 
  .[[1]] %>% 
  get_pldat(., 'Temp')

p3 <- ggplot() +
  geom_line(data = pl3[[1]], aes(x = Ara, y = SOD, group = Temp, colour = Temp), size = 1) + 
  geom_text(data = pl3[[2]], aes(x= x, y = y, label = lab), hjust = 0) +
  theme_bw() +
  scale_x_continuous(expression(Omega[Ar])) +
  scale_colour_gradientn(colours = cols) + 
  scale_y_continuous('SOD') +
  ggtitle("(c) Negative additive effect of temperature on \naragonite saturation")

grid.arrange(p1, p2, p3, ncol = 2)

```
Fig. 3 Examples of model interactions of co-occuring environmental variables on cellular response measures.  Each subplot shows a different relationship as either additive or synergistic effects between the variables. All y-axes are transformed to conform to model output. Covarying environmental variables were held constant at the minimum, 25th, median, 75th, and maximum values in the observed data.

```{r effphy, fig.height = 4, fig.width = 9}

# physio 4 (abu, o2, pco2 - pos additive), 38 (dis, ara, t - syn)
physel <- phymod %>% 
  filter(Model %in% paste0('mod', c(4, 38))) %>% 
  dplyr::select(-data)

cols <- RColorBrewer::brewer.pal(9, 'RdBu')

# mod 4 physio (abu, o2, pco2 - pos additive)
pl4 <- filter(physel, grepl('4$', Model)) %>% 
  .$Modobj %>% 
  .[[1]] %>% 
  get_pldat(., 'O2', fct = 0.85)

p4 <- ggplot() +
  geom_line(data = pl4[[1]], aes(x = pCO2, y = abu, group = O2, colour = O2), size = 1) + 
  geom_text(data = pl4[[2]], aes(x= x, y = y, label = lab), hjust = 0) +
  theme_bw() +
  scale_colour_gradientn(colours = cols) + 
  scale_y_continuous('Abundance') +
  ggtitle("(a) Positive additive effect of O2 on\npCO2 stress")

# mod 38 physio (dis, ara, t - syn)
pl5 <- filter(physel, grepl('38$', Model)) %>% 
  .$Modobj %>% 
  .[[1]] %>% 
  get_pldat(., 'Temp', 'right', fct = 1.05)

p5 <- ggplot() +
  geom_line(data = pl5[[1]], aes(x = Ara, y = dis, group = Temp, colour = Temp), size = 1) + 
  geom_text(data = pl5[[2]], aes(x= x, y = y, label = lab), hjust = 1) +
  theme_bw() +
  scale_colour_gradientn(colours = cols) + 
  scale_y_continuous('Shell dissolution') +
  scale_x_continuous(expression(Omega[Ar])) +
  ggtitle("(b) Synergistic effect of temperature on \naragonite saturation")

grid.arrange(p4, p5, ncol = 2)
```
Fig. 4 Examples of model interactions of co-occuring environmental variables on abundance and shell dissolution. Each subplot shows a different relationship as either additive or synergistic effects between the variables. All y-axes are transformed to conform to model output. Covarying environmental variables were held constant at the minimum, 25th, median, 75th, and maximum values in the observed data.
